Continuous-Time Markov Chain with Alarms analysis and comparison of tools \thanks{This paper has been written in the context of my internship at the Faculty of Informatics with Vojt\v{e}ch \v{R}eh{\'{a}}k at the Masaryk University}

### 2018-07-24 Report/report/paper.tex
institution final version

\begin{document}
%
\title{Continuous-Time Markov Chain with Alarms analysis and comparison of tools \thanks{This paper has been written in the context of my internship at the Faculty of Informatics with Vojtech Reh{\'{a}}k at the Masaryk University}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Thomas Mari\inst{1,2}}%\orcidID{0000-1111-2222-3333}}
%
\titlerunning{ACTMC analysis and comparison of tools}% Part of RIGHT running header
\authorrunning{Thomas Mari}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{ENS-Rennes, Campus de Ker lann, Avenue Robert Schuman, 35170 Bruz, France \and
Masaryk University, Botanická 68A, 602 00 Brno-Královo Pole, Czech republic
\email{thomas.mari@ens-rennes.fr}\\
\url{http://perso.eleves.ens-rennes.fr/people/thomas.mari/}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
For the analysis of ACTMC, Phase-type fitting is the advised way of modeling non-Markovian distributions within PRISM model checker. We ran experimental computations and deduced a reliable way of obtaining precise analysis results for phase-type fitted PRISM CTMCs.
We aim to compare Phase-type fitting with other approaches that handle directly the non-Marlovian distributions in term of efficiency and precision.

@@

\subsubsection*{Acknowledgements}
I would like to thank Vojtech Reh{\'{a}}k, which has been  my supervisor during this internship. Also, I thank M\'{a}rio Uhr\'{i}k for his assistance during this internship and our joint contributions and discussions.

@@

\end{thebibliography}
\fi
\section*{Annexe}
\printbibliography

>>>>

\begin{document}
%
\title{Continuous-Time Markov Chain with Alarms analysis and comparison of tools \thanks{This paper has been written in the context of my internship at the Faculty of Informatics with Vojt\v{e}ch \v{R}eh{\'{a}}k at the Masaryk University}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Thomas Mari\inst{1,2}}%\orcidID{0000-1111-2222-3333}}
%
\titlerunning{ACTMC analysis and comparison of tools}% Part of RIGHT running header
\authorrunning{Thomas Mari}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{ENS-Rennes, Campus de Ker lann, Avenue Robert Schuman, 35170 Bruz, France \and
Masaryk University, Botanická 68A, 602 00 Brno-Královo Pole, Czech republic
\email{thomas.mari@ens-rennes.fr}\\
\url{http://perso.eleves.ens-rennes.fr/people/thomas.mari/}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
For the analysis of ACTMC, Phase-type fitting is the advised way of modeling non-Markovian distributions within PRISM model checker. We ran experimental computations and deduced a reliable way of obtaining precise analysis results for phase-type fitted PRISM CTMCs.
We aim to compare Phase-type fitting with other approaches that handle directly the non-Marlovian distributions in term of efficiency and precision.

@@

\subsubsection*{Acknowledgements}
I would like to thank Vojt\v{e}ch \v{R}eh{\'{a}}k, which has been  my supervisor during this internship. Also, I thank M\'{a}rio Uhr\'{i}k for his assistance during this internship and our joint contributions and discussions.

@@

\end{thebibliography}
\fi

\printbibliography
